%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Cover Letter
% XeLaTeX Template
% Version 1.1 (24/12/18)
%
% This template has been downloaded from:
% https://github.com/mlda065/friggeri-letter
%
% Original author:
% Matthew Davis, based on code by
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
%    Copyright (C) 2012, Adrien Friggeri
%    Permission is hereby granted, free of charge, to any person obtaining a
%    copy of this software and associated documentation files (the "Software"),
%    to deal in the Software without restriction, including without limitation
%    the rights to use, copy, modify, merge, publish, distribute, sublicense,
%    and/or sell copies of the Software, and to permit persons to whom the
%    Software is furnished to do so, subject to the following conditions:
%    The above copyright notice and this permission notice shall be included in
%    all copies or substantial portions of the Software. THE SOFTWARE IS
%    PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%    IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%    FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%    AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%    LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
%    FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER
%    DEALINGS IN THE SOFTWARE.
%
% Important notes:
% This template needs to be compiled with XeLaTeX
% You may need to compile twice for the header to appear.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,english]{friggeri-letter}

\usepackage{babel}

\begin{document}

\header{Francesco}{Argentieri}{junior mechanic engineer}

\address{
   Circonvallazione Istoniense, 20 \\
   Vasto (CH), 66054 \\
   Italy
}


\letter{
   Renault Sport\\
}


\opening{Dear HR}

I am writing to you to express interest in application for systems modelling engineer 
position as advertised on Linkedin and renaultsport.com. I am at the
time of completing my studies to obtain the M.Sc in mechatronic engineering.
Having already a bachelor's degree in mechanical engineering.

During my university career I have always developed projects both in groups and
individually, always reaching the best goals and achieving all the required
objectives.

I acquired skills in the use of design and modeling in suites like Ansys. I have
matured experience in using Matlab and its advanced use integrated with other
software. I also have a good knowledge of symbolic manipulation software such as
Maple. I can briefly learn new software.

Even if I am completing the M.Sc., I have developed a critical thinking, the
ability to analyze and to propose the best solution as well as the ability to
work in a team. I offer my skills, but above all my desire to start working,
experimenting and growing professionally.

Thank you for your time and consideration.

\closing{
   Yours Sincerely\\
   Francesco Argentieri}

\end{document}
